Draft_Application_Stochastic_Volatility

### 2021-07-16 Real Dataset SV.Rmd
update

\section{Overview}
In the following sections, we will try to replicate some of the analyses which were previously conducted on synthetic data, generated by a basic stochastic volatility model; this time, the same model specification and filters will be used on real data. However, as we will see, real data require different strategies to evaluate the effectiveness of several Sequential Monte Carlo techniques. Intuitively, such differences are due to the fact that now the latent process driving the Hidden Markov Model is not observed, nor do we know exactly its law of motion. 
This part of the work is structured as follows: section \textit{fill with the number of the section} provides a review of recent research in the stochastic volatility literature, including extensions of the basic specification and the use of particle filters; section \textit{fill with the number of the section} describes the data which we employ and the transformations that were applied to them. In section \textit{fill with the number of the section} several particle filters are compared in terms of computational cost in approximating the filtering distribution implied by our SV model. Section \textit{fill with the number of the section} features a forecast comparison between two SV specifications and a model that assumes constant mean and variance for the financial returns, namely a forecasting exercise that would not be possible were it not for particle filtering techniques. In section \textit{fill with the number of the section} we conclude by employing a non-parametric measure of realised volatility as a proxy for the latent volatility process, allowing a RMSE and MAE comparison between filters which is similar to that of section \textit{fill with the number of the section} for synthetic data.

>>>>

\section{Overview}
In the following sections, we will try to replicate some of the analyses which were previously conducted on synthetic data, generated by a basic stochastic volatility model; this time, the same model specification and filters will be used on real data. However, as we will see, real data require different strategies to evaluate the effectiveness of several Sequential Monte Carlo techniques. Intuitively, such differences are due to the fact that now the latent process driving the Hidden Markov Model is not observed, nor do we know exactly its law of motion. 
This part of the work is structured as follows: section \textit{fill with the number of the section} provides a review of recent research in the stochastic volatility literature, including extensions of the basic specification and the use of particle filters; section \textit{fill with the number of the section} describes the data which we employ and the transformations that were applied to them. In section \textit{fill with the number of the section} we briefly compare the series of filtered states that are obtained from different particle filters; moreover, several PFs are compared in terms of computational cost in approximating the exact filtering distribution implied by our SV model. Section \textit{fill with the number of the section} features a forecast comparison between two SV specifications and a model that assumes constant mean and variance for the financial returns, namely a forecasting exercise that would not be possible were it not for particle filtering techniques. In section \textit{fill with the number of the section} we conclude by employing a non-parametric measure of realised volatility as a proxy for the latent volatility process, allowing a RMSE and MAE comparison between filters which is similar to that of section \textit{fill with the number of the section} for synthetic data.
